Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-05 ms.tex
salvaged appendix A
blah

We crudely account for the expected suppression of SN Ia heating resulting from its non-steady nature by setting $v_{w}^{\rm Ia} = 0$ when the stagnation radius (calculated excluding Ia heating) exceeds the Ia radius $r_{\rm Ia}$ exterior to which the interval between subsequent supernovae exceeds the local dynamical time (eq.~[\ref{eq:rIa}]).  Finally, note that $v_{\rm w}^{\rm C}$ and $v_{\rm w}^{\rm Ia}$ also depend on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us to simultaneously solve a series of implicit equations to determine each heating rate.  Heating from MSPs is found to be negligibly small for fiducial parameters and hence is not shown, while kinetic feedback is neglected given its uncertain efficiency ($\S\ref{sec:kinetic}$).

@@

Similar cyclic AGN activity could occur on the smaller radial scale of the sphere of influence (e.g.~\citealt{Yuan&Li11}, \citealt{Cuadra+15}).  In this case the large scatter in the X-ray luminosities shown in Fig \ref{fig:miller} could result from
the wide range of inflow rates experienced over the course of a cyclic episode between instabilities and periodic nuclear outbursts.  Due to their deeper potential wells, we find that core galaxies are more likely to possess higher accretion
rates and potentially be thermally unstable for a fixed wind heating rate than cusp galaxies.  This could help explain why core galaxies show a wide range of nuclear radio and X-ray luminosities (suggesting cyclic accretion episodes), while cusp galaxies are confined below a threshold (e.g., \citealt{Bender+89, Pellegrini99,   Capetti&Balmaverde05}), consistent with thermally-stable, steady-state picture. ({\bf AG: This picture may be dubious...Review
  the literature but I think that the higher upper bound for cores is
  just due to a mass selection effect.  BDM: The ghost of Balmaverde disagrees.})

>>>>

We crudely account for the expected suppression of SN Ia heating
resulting from its non-steady nature by setting $v_{w}^{\rm Ia} = 0$
when the stagnation radius (calculated excluding Ia heating) exceeds
the Ia radius $r_{\rm Ia}$ exterior to which the interval between
subsequent supernovae exceeds the local dynamical time
(eq.~[\ref{eq:rIa}]) {\bf AG have not yet done this in the impulsive limit}.  Finally, note that $v_{\rm w}^{\rm C}$ and
depends on the total heating rate (eq.~[\ref{eq:vtot}]), requiring us
to simultaneously solve a series of implicit equations to determine
each heating rate.  Heating from MSPs is found to be negligibly small
for fiducial parameters and hence is not shown, while kinetic feedback
is neglected given its uncertain efficiency ($\S\ref{sec:kinetic}$).

@@

Similar cyclic AGN activity could occur on the smaller radial scale of
the sphere of influence (e.g.~\citealt{Yuan&Li11},
\citealt{Cuadra+15}).  In this case the large scatter in the X-ray
luminosities shown in Fig \ref{fig:miller} could result from the wide
range of inflow rates experienced over the course of a cyclic episode
between instabilities and periodic nuclear outbursts.  Due to their
deeper potential wells {\bf AG: Cores don't necessarily have deeper
  potential wells overall}, we find that core
galaxies are more likely to possess higher accretion rates and
potentially be thermally unstable for a fixed wind heating rate than
cusp galaxies.  This could help explain why core galaxies show a wide
range of nuclear radio and X-ray luminosities (suggesting cyclic
accretion episodes), while cusp galaxies are confined below a
threshold (e.g., \citealt{Bender+89, Pellegrini99,
  Capetti&Balmaverde05}), consistent with thermally-stable,
steady-state picture. ({\bf AG: This picture may be dubious...Review
  the literature but I think that the higher upper bound for cores is
  just due to a mass selection effect.  BDM: The ghost of Balmaverde
  disagrees.})
